Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-09 man/figures/browning.Rmd
update figure browing

```{r, echo=FALSE}
show_text <- FALSE
```
##### 
**Appendix S4.** Percentage of pixels showing browning, greenning or no-changes during the 2005 and 2012 droguht events according to EVI standardized anomalies.

@@

per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat='identity', position = "dodge") + 
  # geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=3, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "black", fill = "white")
        ) + labs(fill = 'Drought event') + scale_fill_manual(values = c("#DAA520", "#104E8B")) +
  scale_y_continuous(expand=c(.1,0)) + 
  geom_text_repel(aes(label = paste0(per, " %")), 
                  position=position_dodge(width=0.9))

>>>>

```{r, echo=FALSE}
show_text <- FALSE
```
##### 
**Appendix S4.** Percentage of pixels showing browning, greenning or no-changes during the 2005 and 2012 drought events according to EVI standardized anomalies.

@@

per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat='identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=4, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "white", fill = "white"),
        strip.text = element_text(size = 12), 
        axis.title.y = element_text(size = 14, face = 'bold'),
        axis.text = element_text(size = 11),
        panel.grid = element_blank(),
        legend.position = 'bottom') + 
  labs(fill = 'Drought event') + 
  scale_fill_colorblind() + 
  scale_y_continuous(limits = c(0, 110), breaks = c(0, 25, 50, 75, 100))
